Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
adding my comment.
supply markup credits to our contributions.

\begin{itemize}
\item
    We originally implemented Doctest in Haskell, back in 2010.
\item
    Add support for QuickCheck properties to Doctest (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

We are grateful to David Waern, Haddock's maintainer, for reviewing our patches
and accepting our patches to Haddock.
We would like to thank
Nick Smallbone for having improved QuickCheck so that
non-quantified properties are tested just once.

>>>>

\begin{itemize}
\item
    We originally implemented Doctest in Haskell and
    extended Haddock markup to support examples, back in 2010
\item
    Add support for QuickCheck properties to Doctest and
    extend Haddock markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

We are grateful to David Waern, Haddock's maintainer, for reviewing our patches
and accepting our patches to Haddock.

\begin{quote}
  kazu: this seems redundant: how about "\emph{for reviewing and accepting our patches}"?
\end{quote}

We would like to thank
Nick Smallbone for having improved QuickCheck so that
non-quantified properties are tested just once.
